Phylogenetic inference of contact network parameters with approximate Bayesian computation

### 2016-07-14 doc/defence/posterior1.tex
Presentation

\begin{frame}{Marginal posterior distributions for $\alpha$ show least spread}
  \begin{minipage}[p][\textheight][t]{\textwidth}
    \begin{center}
    preferential attachment power \hfill prevalence
      \includegraphics[width=0.8\textwidth]{abc-posterior-example.pdf}

      \vspace{-0.25cm}
      edges per vertex \hfill total nodes
    \end{center}
  \end{minipage}
\end{frame}

>>>>

\begin{frame}{Marginal posterior distributions for $\alpha$ show least spread}
  \vspace{-0.5cm}
  \begin{tikzpicture}
    \node at (0, 0) [anchor=center] {\includegraphics[trim=1cm 0 0 0, clip, width=0.8\textwidth]{{abc-posterior/1.0_1000_3_5000_0}.pdf}};
    \node at (-4, 3) [anchor=center, text width=2cm, fill=white, inner sep=2pt] {preferential attachment};
    \node at (4.5, 3) [anchor=center, text width=2cm, fill=white, inner sep=2pt] {number infected};
    \node at (-4.2, -1) [anchor=center, text width=2cm, align=center, fill=white, inner ysep=2pt, inner xsep=0pt] {edges per vertex};
    \node at (4.2, -0.7) [anchor=center, text width=1.5cm, align=center, fill=white, inner sep=2pt] {total nodes};

    \only<1>{ \fill [white] (0, 0) rectangle (4.8, 3.8);}
    \only<1-2>{ \fill [white] (0, 0) rectangle (-5, -3.8);}
    \only<1-3>{ \fill [white] (0, 0) rectangle (4.8, -3.8);}
    \only<4>{ }
  \end{tikzpicture}
\end{frame}

### 2016-07-14 doc/defence/presentation.tex
Presentation

\usetheme[everytitleformat=regular]{m}
%\setbeamertemplate{navigation symbols}{}

@@

%\begin{frame}{Outline}
%    \tableofcontents
%\end{frame}

%\section{Background and Motivation}
%\input{contactnet}
%\input{phylo}
%\input{objects}
%\input{transtree}
%\input{virusphylo}
%\input{inference}
%%\input{netmodel}
%\input{why}

%\section{The Barab\'asi-Albert (BA) Contact Network Model}
%\input{ba}
%\input{identifiable}
%\input{kpca}

%\section{\textit{Netabc}: Phylogenetic Reconstruction of Contact Network Parameters with Approximate Bayesian Computation}
%\input{smc}
%\input{posterior1}
%\input{posterior2}
%\input{pointest}
%\input{pointest2}

\section{Application to real HIV epidemics}
\input{data}

\section{Conclusions}

\end{document}

\begin{frame}{HIV networks have sub-linear preferential attachment}
    Also, higher PA for IDU networks.

    \includegraphics[trim=0 3.5in 3.3in 0, clip, width=0.5\textwidth]{realdata-hpd-bc}
    \includegraphics[trim=3.4in 1.5in 0 2.0in, clip, width=0.5\textwidth]{realdata-hpd-bc}
\end{frame}

\begin{frame}{Conclusions}
  \begin{itemize}
    \item We developed a phylodynamic method to fit contact network models to
      phylogenetic data.
      \pause
    \item The preferential attachment power of the Barab\'asi-Albert network
      model, which is challenging to estimate by traditional epidemiological
      methods, can be estimated with ABC.
      \pause
    \item The networks underlying real epidemics are heterogeneous,
      underscoring the importance of considering network structure in
      phylodynamic analyses.
  \end{itemize}
\end{frame}

\begin{frame}{Acknowledgements}
  \begin{columns}
    \begin{column}{0.6\textwidth}

      \textbf{BC Centre for Excellence in HIV/AIDS}

      Art Poon

      Jeff Joy

      Richard Liang

      Thuy Nguyen

      P. Richard Harrigan

      \hfill\\
      \textbf{University of British Columbia}

      Sarah Otto

      Alexandre Bouchard-C\^ot\'e

      \vfill
      \vspace{0.5cm}
      $\qquad\qquad$\includegraphics[width=2cm]{logos/genomecanada}
      $\qquad$
      \includegraphics[width=2cm]{logos/genomequebec}
    \end{column}
    \begin{column}{0.4\textwidth}
      \centering

      \includegraphics[width=3cm]{logos/cfe}
      \vspace{0.5cm}

      \includegraphics[width=3cm]{logos/cihr}

      \includegraphics[width=3cm]{logos/genomebc}

      \includegraphics[width=3cm]{logos/bmgf}
      \vspace{0.5cm}

      \includegraphics[width=3cm]{logos/btp}
    \end{column}
  \end{columns}
\end{frame}

\end{document}

>>>>

\usetheme[everytitleformat=regular]{m}
\setbeamertemplate{navigation symbols}{}

@@

\begin{frame}{Outline}
    \tableofcontents
\end{frame}

\section{Background and motivation}
\input{contactnet}
\input{phylo}
\input{objects}
\input{transtree}
\input{virusphylo}
\input{inference}
%\input{netmodel}
\input{why}

\section{The Barab\'asi-Albert (BA) contact network model}
\input{ba}
\input{identifiable}
\input{kpca}

\section{Our inference method: \itshape{netabc}}
\input{abc}
\input{smc}
\input{posterior1}
\input{posterior2}
\input{pointest}
\input{pointest2}

\section{Application to real HIV epidemics}
\input{map}
\input{realdata}

\section{Conclusions}
\input{conclusions}

\input{acknowledgements}

\input{supp}
\end{document}
